---
title: "Multiple Regression Lab"
author: "Suprita Bhomkar"
date: "10/20/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath("/Users/supritabhomkar/Desktop/540 in class/Lab 2- Multiple regresssion"))
```


```{r library }
options(scipen=10000)
library(readxl)
library(tidyverse)
library(mi)
```

```{r Data}
MRLabData <- read_excel("MRLabdata.xlsx")
```

Scatterplots for dependent variable as Price and all other independent variable

```{r scatterplots}
ggplot(data=MRLabData, aes(x=BEDS, y=PRICE)) + geom_point(size=2)
ggplot(data=MRLabData, aes(x=BATHS, y=PRICE)) + geom_point(size=2)
ggplot(data=MRLabData, aes(x=`SQUARE FEET`, y=PRICE)) + geom_point(size=2)
ggplot(data=MRLabData, aes(x=`YEAR BUILT`, y=PRICE)) + geom_point(size=2)
ggplot(data=MRLabData, aes(x=`LOT SIZE`, y=PRICE)) + geom_point(size=2)

```



*Histograms for all the variables
```{r histograms}
hist(MRLabData$BEDS)
hist(MRLabData$BATHS)
hist(MRLabData$`SQUARE FEET`)
hist(MRLabData$`YEAR BUILT`)
hist(MRLabData$`LOT SIZE`)
hist(MRLabData$PRICE)
```


GGplot with Geomsmooth
```{r }
ggplot(data=MRLabData, aes(x=BEDS, y=PRICE)) + geom_point(size=2)+geom_smooth()
ggplot(data=MRLabData, aes(x=BATHS, y=PRICE)) + geom_point(size=2)+geom_smooth()
ggplot(data=MRLabData, aes(x=`SQUARE FEET`, y=PRICE)) + geom_point(size=2)+geom_smooth()
ggplot(data=MRLabData, aes(x=`YEAR BUILT`, y=PRICE)) + geom_point(size=2)+geom_smooth()
ggplot(data=MRLabData, aes(x=`LOT SIZE`, y=PRICE)) + geom_point(size=2)+geom_smooth()

```


```{r selectsubset}
MRLAB2 <- MRLabData %>% select(PRICE,BEDS,BATHS,`SQUARE FEET`,`LOT SIZE`,`YEAR BUILT`)
```


Delete missing data
```{r deleteMissing}
summary(MRLAB2)
MRLAB3 <-  MRLAB2[complete.cases(MRLAB2), ]

```

Regression 1 with all the variables
```{r Regression1}
HouseFit1<-lm(PRICE~BATHS+BEDS+`SQUARE FEET`+`LOT SIZE`+ `YEAR BUILT`, data=MRLAB3)
summary(HouseFit1)
```


Regression with selected Significant variables
```{r Regression2}
HouseFit2<-lm(PRICE~BEDS+`SQUARE FEET`+`YEAR BUILT`, data=MRLAB3)
summary(HouseFit2)
```



```{r Regression3}
HouseFit3<-lm(PRICE~`SQUARE FEET`,data=MRLAB3)
summary(HouseFit3)
```


Residuals for Model 1
```{r Residuals1}

plot(HouseFit1)

Price.stdres1 <-residuals(HouseFit1)

ggplot(data=MRLAB3, aes(x=BEDS, y=Price.stdres1))+geom_point()
ggplot(data=MRLAB3, aes(x=BATHS, y=Price.stdres1))+geom_point()
ggplot(data=MRLAB3, aes(x=`SQUARE FEET`, y=Price.stdres1))+geom_point()
ggplot(data=MRLAB3, aes(x=`LOT SIZE`, y=Price.stdres1))+geom_point()
ggplot(data=MRLAB3, aes(x=`YEAR BUILT`, y=Price.stdres1))+geom_point()
```

Residuals for Model 2
```{r Residual2}
plot(HouseFit2)

Price.stdres2 <-residuals(HouseFit2)

ggplot(data=MRLAB3, aes(x=BEDS, y=Price.stdres2))+geom_point()
ggplot(data=MRLAB3, aes(x=BATHS, y=Price.stdres2))+geom_point()
ggplot(data=MRLAB3, aes(x=`SQUARE FEET`, y=Price.stdres2))+geom_point()
ggplot(data=MRLAB3, aes(x=`LOT SIZE`, y=Price.stdres2))+geom_point()

```

Residual for Model 3
```{r Residual3}
plot(HouseFit3)
Price.stdres3 <-residuals(HouseFit3)
ggplot(data=MRLAB3, aes(x=`SQUARE FEET`, y=Price.stdres3))+geom_point()

```


Logging the variables
```{r logs}
MRLAB3$LOGPRICE <- log(MRLAB3$PRICE)
MRLAB3$LOGSqFoot <- log(MRLAB3$`SQUARE FEET`)
MRLAB3$LOGLotSize <- log(MRLAB3$`LOT SIZE`)
MRLAB3$LOGYearBuilt <- log(MRLAB3$`YEAR BUILT`)
```

Linear model after Logging
```{r RegLog}

HouseFitlog<-lm(LOGPRICE~BATHS+BEDS+LOGSqFoot+LOGLotSize+LOGYearBuilt, data=MRLAB3)
summary(HouseFitlog)
```

Residual after logging
```{r ResidLog}
PriceLOG.stdres <-residuals(HouseFitlog)

ggplot(data=MRLAB3, aes(x=BEDS, y=PriceLOG.stdres))+geom_point()
ggplot(data=MRLAB3, aes(x=BATHS, y=PriceLOG.stdres))+geom_point()
ggplot(data=MRLAB3, aes(x=LOGSqFoot, y=PriceLOG.stdres))+geom_point()
ggplot(data=MRLAB3, aes(x=LOGLotSize, y=PriceLOG.stdres))+geom_point()
ggplot(data=MRLAB3, aes(x=LOGYearBuilt, y=PriceLOG.stdres))+geom_point()
```

Predictions

```{r predictions}
Price.predict=predict(lm(PRICE~BATHS+BEDS+`SQUARE FEET`+`LOT SIZE`+`YEAR BUILT`, data=MRLAB3))

```

```{r predictedvsActual}
ggplot(MRLAB3, aes(x = BEDS, y = PRICE)) +
  geom_point()+ # Points of actual values
  geom_point(aes(y = Price.predict), shape = 1)  # Points of predicted values

ggplot(MRLAB3, aes(x = BATHS, y = PRICE)) +
  geom_point()+ # Points of actual values
  geom_point(aes(y = Price.predict), shape = 1) # Points of predicted values

ggplot(MRLAB3, aes(x = `SQUARE FEET`, y = PRICE)) +
  geom_point()+ # Points of actual values
  geom_point(aes(y = Price.predict), shape = 1) # Points of predicted values

ggplot(MRLAB3, aes(x = `LOT SIZE`, y = PRICE)) +
  geom_point()+ # Points of actual values
  geom_point(aes(y = Price.predict), shape = 2) # Points of predicted values

ggplot(MRLAB3, aes(x = `YEAR BUILT`, y = PRICE)) +
  geom_point()+ # Points of actual values
  geom_point(aes(y = Price.predict), shape = 3) # Points of predicted values


```


Imputations
```{r}
mMRLab<-missing_data.frame(data.frame(MRLAB2))

show(mMRLab)

summary (mMRLab)

imputations <- mi(mMRLab, n.iter = 30, n.chains = 4, max.minutes = 20) 
show(imputations)
round(mipply(imputations, mean, to.matrix = TRUE), 3)
imputations <- mi(imputations, n.iter = 5)
plot(imputations)

Houseanalysis <- pool(PRICE ~ BEDS + BATHS + SQUARE.FEET + YEAR.BUILT + LOT.SIZE, data = imputations, m = 5)

display(Houseanalysis)
```


